\begin{acknowledgements}
  % \lipsum[1]
\OnehalfSpacing

\noindent

It has been a real pleasure to work on this topic for the last three years. Thanks first of all to Ray for taking me on with such an interesting project, for encouraging me to follow the avenues that led to the different parts of this thesis, and for your encyclopaedic knowledge of any subject we worked on.

Thanks to everyone in the group, which has given me friends and support that I couldn't have imagined when I started. In particular, thanks to Graham, Neil, Shami, and Tim for distractions from work, fun times away at conferences, and the occasional collaboration. It has been so exciting to see the group develop in my time here, and I can't wait to see what it can achieve.

Thanks to STFC, Hertford College, and AOPP for all of the financial support and administrative help that made this DPhil possible. I feel very lucky to have been supported by, and a part of, these institutions.

Thanks to my friends at Hertford, those around Oxford, and everyone else who has made my time here such fun. Holidays, dinners, squash, croquet, bops, punting, dog walks, and Pango Pong have all been more important to this thesis than any pseudo-spectral method. Thanks especially to Antonis, Maj, Phoebe, Georgia, Adam, Sacha, Dáire, and everyone from Pembroke. Thank you Mann, for making me so happy, supporting me every day, and even eventually remembering the name of the planet I'm researching.

Finally, thanks most of all to my family. I have always felt encouraged to do whatever interested me, and I am so grateful for all of the support I have had in going down this path.

\DoubleSpacing


  %%%%%%%
%
% It has been a pleasure to work on this topic for the last three years. Thanks to Ray for taking me on, supporting every part of this thesis, and giving me the freedom to follow interesting avenues as they appeared.
%
% The Planetary Climate group has grown from two people to over a dozen, and is now a great source of friends and collaboration, both of which I hope will continue for many years. Particular thanks for the work in this thesis should go to Graham for the modelling work we have done together, and to Neil, Shami, and Tim for many conversations about new ideas and general distractions from work.
%
%
% It is never possible to adequately thank everyone who makes a place special or supports you through a time of life, so I hope that everyone who did that knows it. Thanks to my friends at Hertford and around Oxford, who have been a continual source of fun and distraction.
%
% Finally, the most important thanks must go to my family, for supporting me down this path.



\end{acknowledgements}
