\begin{SingleSpace}
\chapter{Clouds on Lava Planets}\label{ch:clouds-lava-planets}
\vspace{0.5cm}
\chapterprecishere{``One face is forever sunlit, and one forever dark, and only the planet's slow liberation gives the twilight zone a semblance of seasons.''\par\raggedleft--- \textup{Stanley G. Weinbaum}, The Lotus Eaters}
\end{SingleSpace}
\vspace{0.5cm}





% 0 -- LEAD-IN PARAGRAPHS

%START ELEMENT
Cloud-covered exoplanets are a great problem for exoplanet observers, turning illuminating spectra into flat lines. Uniform cloud cover can be an issue, but heterogenous cloud cover may be useful.



%FRAMING TEXT
Hot Jupiters are suggested to have cloud cover. Lava planets could have

%SIGNPOSTS


%SUMMARISE CONCLUSIONS
In this chapter, I address the outstanding question from Chapter X -- could the difference between our model results of 55 Cancri e and the observed low night-side temperature be due to high night-side clouds? I also discuss the effect of clouds on global circulation and on observables such as hot-spot shift.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%SECTION 1 --
\section{Clouds on Lava Planets}

Outgassing


%SUBSECTION --

%SUBSECTION --

%SECTION CONCLUSIONS



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%SECTION 2 --
\section{Methods}


%SUBSECTION --
\subsection{SOCRATES Radiative Transfer}

To represent the effect of clouds accurately, we needed a more sophisticated radiative transfer scheme than the semi-grey scheme used in previous chapters. We coupled the correlated-k radiative transfer code SOCRATES to Exo-FMS \citep{Edwards1996socrates}. See Appendix X for more details.

%SUBSECTION --
\subsection{DIHRT Dynamical Clouds}

%SECTION CONCLUSIONS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%SECTION 3 --
\section{Simulations with Socrates}

We ran simulations with Socrates.

Test 1 with CO

Test 2 with CO and CO2 for SW

Compare to Test X with grey gas


%SUBSECTION --
\subsection{Comparison with Grey-Gas}

Temperature maps

Zonal wind

%SUBSECTION --
\subsection{Simulated Observations}

Phase curves

%SECTION CONCLUSIONS


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%SECTION 4 --
\section{Cloudy Simulations}


%SUBSECTION --
\subsection{Pure CO Atmosphere}

%SUBSECTION --
\subsection{Pure CO Atmosphere with Na}

%SUBSECTION --
\subsection{Pure CO Atmosphere with H2O}

%SUBSECTION --
\subsection{H2 Atmosphere}

%SECTION CONCLUSIONS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%SECTION 5 --
\section{Discussion}

%SUBSECTION --
\subsection{Implications for Climate}

%SUBSECTION --
\subsection{Implications for Observations}

%CONCLUSIONS

%RESTATE SECTION CONCLUSIONS

%OPEN OUT CONCLUSIONS


% \bibliographystyle{unsrtnat}
% \bibliography{../references.bib}
