\begin{SingleSpace}
\chapter{Comparing Lava Planets}
\vspace{0.5cm}
\chapterprecishere{``Any finite number divided by infinity is as near to nothing as makes no odds, so the average population of all the planets in the Universe can be said to be zero. From this it follows that the population of the whole Universe is also zero, and that any people you may meet from time to time are merely the products of a deranged imagination.''\par\raggedleft--- \textup{Douglas Adams}, The Restaurant at the End of the Universe}
\end{SingleSpace}
\vspace{0.5cm}

This thesis has focused on one planet, 55 Cancri e. In the near future, many more observations of the atmospheres of lava planets, Hot Jupiters, and other tidally locked exoplanets will be made.

In this chapter, I simulate the atmospheres of two planets which will soon be observed, K2-141b and LH dS 3844b. I compare the expected phase curves, hot-spot shifts, and day-night temperature contrasts. Comparing observational features of many different planets will let us test the predictions of the simulations and simplified theories discussed in this thesis.

\section{55 Cancri e}

Figure X shows a control simulation for 55 Cancri e.

\section{K2-141b}

Figure X shows a control simulation for K2-141b. This planet is smaller and hotter than 55 Cancri e, with a more rapid rotation rate.

\section{LHS 3844b}

Figure X shows a control simulation for LHS 3844b.


In this chapter, I have shown how the shallow-water theory discussed in chapter X can predict the comparative differences between observations and simulations of lava planets.




% \bibliographystyle{unsrtnat}
% \bibliography{../references.bib}
