\begin{SingleSpace}
\chapter{Simulating Tidally Locked Exoplanets with Exo-FMS}\label{ch:sim-exofms}
\vspace{0.5cm}
\chapterprecishere{``One face is forever sunlit, and one forever dark, and only the planet's slow liberation gives the twilight zone a semblance of seasons.''\par\raggedleft--- \textup{Stanley G. Weinbaum}, The Lotus Eaters}
\end{SingleSpace}
\vspace{0.5cm}




% 0 -- LEAD-IN PARAGRAPHS

%START ELEMENT
Three-dimensional simulations are an important tool for understanding atmospheric dynamics and climate.

A General Circulation Model (GCM)


%FRAMING TEXT
This chapter describes my work on the GCM Exo-FMS, and discusses the specific needs and issues of the atmospheres that I simulated with it.

%SIGNPOSTS
I will discuss the dynamical core and grid of the model

%SUMMARISE CONCLUSIONS
This chapter does not include much scientific investigation, but I will try to show that an exoplanet GCM is not a fanciful attempt to recreate an unknowable planet, but can be used carefully alongside basic theories and real observations to understand processes that are only apparent in a full 3D representation of the planetary atmosphere. I will also argue that XX.

%SECTION 0 -- MODEL STRUCTURE
\section{Model Structure}

%SUBSECTION -- FMS
\subsection*{GFDL-FMS}

Exo-FMS is based on the cubed-sphere dynamical core of the GFDL FMS.


%SUBSECTION -- GITHUB
\subsection*{Github Repository}

It was very important that Exo-FMS should be openly available. I manage its Github repository and wiki.


%SUBSECTION -- NEW INTERFACE
\subsection*{ExoFMS Interface}

Exo-FMS is meant to make the fewest modifications to the original FMS structure and cubed-sphere dynamical core as possible. To this end, I wrote a single interface to couple the dynamical core to our physics modules (radiative transfer, convection etc.).



%SECTION 1 -- DYNAMICS
\section{Dynamics}

%SUBSECTION -- LAT-LON

%SUBSECTION -- CUBED-SPHERE

%SECTION CONCLUSIONS


%SECTION 2 --RADIATIVE TRANSFER
\section{Radiative Transfer}

%SUBSECTION -- GREY-GAS

%SUBSECTION -- SOCRATES

%SECTION CONCLUSIONS


%SECTION 3 -- CLOUDS
\section{Cloud Microphysics}

%SUBSECTION -- DIHRT

%SUBSECTION -- INTERFACE TO SOCRATES

%SECTION CONCLUSIONS


%CONCLUSIONS

%SUBSECTION -- LAVA PLANETS

%SUBSECTION -- EARTH-LIKE PLANETS

%RESTATE SECTION CONCLUSIONS

%OPEN OUT CONCLUSIONS
